How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex
rephrased discussion

@@

\subsubsection{Sharing of Scripts and Procedures}
Investigating the use of clones between programs, we observe that there are 1700 scripts that are used in multiple programs, sometimes as often as in 1600 different programs. This seems to indicate that there are common patterns in Scratch programs, which means it might be very beneficial to Scratch programmers if they could not only share their programs, but also share some of their functionality, for others to use, like a library. An example of such a library could be: functions for platforming games, including the movement of a player, collision detection and the implementation of `lives'. This might empower new Scratch users to get started quicker.

>>>>

\subsubsection{Popularity of Different Block Types}
Our analysis shows that some categories of blocks are rarely used, like the `Pen' blocks, of which only \todo{x} occur within \todo{y} programs. When further evolving the Scratch programming language, this category might be less important to users, and hence our current analysis supports the language designers in making future investments.

@@
